Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-18 Manuscript_draft.Rmd
update forest plot

#create forest plot
p <- ggplot() + 
  geom_point(data = Q2_2_df, #add estimates 
             aes(y = line, 
                 x = estimate),
             fill = "gray", 
             shape = 22, 
             color = "black",
             size = 4) +
  geom_errorbarh(data = Q2_2_df, #add error bars 
                 aes(y = line, 
                     xmin = lower_bound, 
                     xmax = upper_bound), 
                 height=0.3) +
  geom_text(aes(y = c(-1, -1, -1),  #add cols for study, estimates and CIs
                x = c(-0.2, 1.05, 1.12), 
                label=c("Study", "Prop.", "95% CI")), 
            hjust = 0, 
            fontface = "bold") +
  geom_text(data = Q2_2_df, #add estimate labels
            aes(y = line, 
                x = 1.05, 
                label = prop), 
            hjust = 0) +
  geom_text(data = Q2_2_df, #add CI labels
            aes(y = line,
                x = 1.12,
                label = CI), 
            hjust = 0) +
  geom_text(data = Q2_2_df, #add study labels
            aes(y= line, 
                x=-0.2, 
                label = label,
                hjust = 0,
                fontface = fontface)) +
  theme_void() + #remove background
  scale_y_reverse() +
  geom_segment(data = Q2_2_df, #add line below point estimates
               aes(y = max(line) + 1, x = 0, xend = 1, 
                   yend = max(line) + 1)) +
  geom_segment(data = Q2_2_df, #add dash for 0
               aes(y = max(line) + 1, yend = max(line) + 1.3, 
                   x = 0, xend = 0)) +
  geom_segment(data = Q2_2_df, #add dash for 0.25
               aes(y = max(line) + 1, yend = max(line) + 1.3,
                   x = 0.25, xend = 0.25)) +
  geom_segment(data = Q2_2_df, #add dash for 0.5
               aes(y = max(line)+1, yend=max(line) + 1.3,
                   x=0.5, xend=0.5)) +
  geom_segment(data = Q2_2_df, #add dash for 0.75
               aes(y = max(line) + 1, yend = max(line) + 1.3,
                   x=0.75, xend = 0.75)) +
  geom_segment(data = Q2_2_df, #add dash for 1
               aes(y = max(line) + 1, 
                   yend = max(line) + 1.3,
                   x = 1, xend = 1)) +
  geom_text(aes(y = rep(max(Q2_2_df$line) + 2,5), #add numbers to line
                x = 0:4/4, 
                label = c(0.00,0.25,0.5,0.75,1.00))) +
  scale_x_continuous()

@@

#create image file
png(file="forest_Q2_2.png", 
    res=300, 
    height=20, width=50, units="cm")
p
dev.off()

@@

#subset df
Q2_2_table <- Q2_2_table %>%
  select(study, q3_setting)

>>>>

#create forest plot
p <- ggplot() + 
  geom_point(data = Q2_2_df, #add estimates 
             aes(y = line, 
                 x = estimate),
             fill = "gray", 
             shape = 22, 
             color = "black",
             size = 4) +
  geom_errorbarh(data = Q2_2_df, #add error bars 
                 aes(y = line, 
                     xmin = lower_bound, 
                     xmax = upper_bound), 
                 height=0.3) +
  geom_text(aes(y = c(-1, -1, -1),  #add cols for study, estimates and CIs
                x = c(-0.2, 1.05, 1.12), 
                label=c("Study", "Prop.", "95% CI")), 
            hjust = 0, 
            fontface = "bold") +
  geom_text(data = Q2_2_df, #add estimate labels
            aes(y = line, 
                x = 1.05, 
                label = prop), 
            hjust = 0) +
  geom_text(data = Q2_2_df, #add CI labels
            aes(y = line,
                x = 1.12,
                label = CI), 
            hjust = 0) +
  geom_text(data = Q2_2_df, #add study labels
            aes(y= line, 
                x=-0.2, 
                label = label,
                hjust = 0,
                fontface = fontface)) +
  theme_void() + #remove background
  scale_y_reverse() +
  geom_segment(data = Q2_2_df, #add line below point estimates
               aes(y = max(line) + 1, x = 0, xend = 1, 
                   yend = max(line) + 1)) +
  geom_segment(data = Q2_2_df, #add dash for 0
               aes(y = max(line) + 1, yend = max(line) + 1.3, 
                   x = 0, xend = 0)) +
  geom_segment(data = Q2_2_df, #add dash for 0.25
               aes(y = max(line) + 1, yend = max(line) + 1.3,
                   x = 0.25, xend = 0.25)) +
  geom_segment(data = Q2_2_df, #add dash for 0.5
               aes(y = max(line)+1, yend=max(line) + 1.3,
                   x=0.5, xend=0.5)) +
  geom_segment(data = Q2_2_df, #add dash for 0.75
               aes(y = max(line) + 1, yend = max(line) + 1.3,
                   x=0.75, xend = 0.75)) +
  geom_segment(data = Q2_2_df, #add dash for 1
               aes(y = max(line) + 1, 
                   yend = max(line) + 1.3,
                   x = 1, xend = 1)) +
  geom_text(aes(y = rep(max(Q2_2_df$line) + 2,5), #add numbers to line
                x = 0:4/4, 
                label = c(0.00,0.25,0.5,0.75,1.00))) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.25))

@@

#create image file
png(file="forest_Q2_2.png", 
    res=300, 
    height=20, width=30, units="cm")
p
dev.off()

@@

#subset df
Q2_2_table <- Q2_2_table %>%
  select(study, q3_setting)
Q2_2_table$q3_setting <- gsub(";([[:alpha:]])", "; \\1", Q2_2_table$q3_setting)
Q2_2_table$q3_setting <- gsub("/([[:alpha:]])", ", \\1", Q2_2_table$q3_setting)
